%%% Acknowledgments.tex<2> --- 
%% 
%% Filename: Acknowledgments.tex<2>
%% Description: 
%% Author: Ola Leifler
%% Maintainer: 
%% Created: Wed Nov 10 09:45:11 2010 (CET)
%% Version: $Id$
%% Version: 
%% Last-Updated: Tue Jun 21 13:28:03 2016 (+0200)
%%           By: Ola Leifler
%%     Update #: 6
%% URL: 
%% Keywords: 
%% Compatibility: 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Commentary: 
%% 
%% 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Change log:
%% 
%% 
%% RCS $Log$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Code:

\swedishenglish{\chapter*{Författarens tack}}{\chapter*{Acknowledgments}}

Firstly, I would like to express my enormous gratitude to my advisors Adrian Pop and Peter Fritzson for their 
constructive feedback, patience and thoughtful supervision of my Ph.D study and research. It has been an honor to work with 
and learn from them at Linköping University. An extra thank you goes to Peter for giving me the opportunity to pursue this research.

My sincere thanks also goes to the current and former members of PELAB, who have worked to create a comfortable and inspiring working environment where I have learned a lot.
I gratefully acknowledge my colleagues and co-authors for their valuable insights and rewarding technical discussions, which has made an invaluable contribution to the articles 
presented in this thesis. This thesis work would not have been possible without their contribution.

My appreciation extends also to everyone who have contributed to the OpenModelica system. I would also like to thank Brittany Shahmehri for her thorough proofreading of this thesis. 
I have benefited from her valuable comments and suggestions, which substantially has improved this thesis.

Special thanks to Anne Moe for facilitating my work with her extraordinary patience and support through the administrative process. 
My sincere thanks also goes to Lene Rosell, Eva Pelayo Danils, Inger Norén, Åsa Kärrman, Mikaela Holmbäck, and other administrative staff for their support.

My deepest appreciation also goes to my friends (too many to list here but you know who you are!) for providing continuous support and friendship that I needed. 
To Ethiopians in Linköping, from the past to the present, I appreciate the times we share challenges and celebrate joys of life. 

Last but not least, I am thankful to my family for all their love and encouragement. For my parents who raised me with a love of socializing and supporting 
me throughout my life. For my loving and supportive wife, Liya, and my three wonderful children Ruth, Fikir and Noah who provided me unending inspiration. Thank you.


\begin{flushright}
	Alachew Mengist
	
	Link\"{o}ping, Sweden
	
	September 2019
\end{flushright}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgments.tex<2> ends here

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "demothesis"
%%% End: 
